Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/model.tex
Space-saving stuff.
Take out a TODO item.

\begin{figure}
\centering
\begin{subfigure}[b]{0.45\linewidth}
  \begin{tikzpicture}[scale=.8,transform shape,thick]
    \node[vertex] (n1) at (0,0)  {1};
    \node[vertex] (n2) at (2,2)  {2};
    \node[vertex] (n3) at (4,0) {3};
    \node[vertex] (n4) at (2,-2) {4};
    \draw[-stealth] (.4,.4) -- (1.6,1.6);
    \draw[-stealth] (2.4,1.6) -- (3.6,.4);
    \node at (.7,1.1) {$t_1$};
    \node at (3.3,1.1) {$t_2$};
  \end{tikzpicture}
  \caption{Dynamic network data}
\end{subfigure}
\begin{subfigure}[b]{0.45\linewidth}
\begin{tikzpicture}[scale=1,transform shape,thick]
\draw[-stealth] (0,0) -- (0,3);
\draw[-stealth] (0,0) -- (5,0);

@@

We allow the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \propto 1$ and $\sigma_p^2 \sim \mbox{Inv-Gamma}(\alpha_{\sigma},\beta_{\sigma})$.
The cluster assignments are given a non-parameteric prior $z_i \sim \mbox{CRP}(\alpha)$.
{\color{red} TODO: Expand on this?}

>>>>

\begin{figure}
\centering
\begin{subfigure}[b]{0.45\linewidth}
  \begin{tikzpicture}[scale=.65,transform shape,thick]
    \node[vertex] (n1) at (0,0)  {1};
    \node[vertex] (n2) at (2,2)  {2};
    \node[vertex] (n3) at (4,0) {3};
    \node[vertex] (n4) at (2,-2) {4};
    \draw[-stealth] (.4,.4) -- (1.6,1.6);
    \draw[-stealth] (2.4,1.6) -- (3.6,.4);
    \node at (.7,1.1) {$t_1$};
    \node at (3.3,1.1) {$t_2$};
  \end{tikzpicture}
  \caption{Dynamic network data}
\end{subfigure}
\begin{subfigure}[b]{0.45\linewidth}
\begin{tikzpicture}[scale=.8,transform shape,thick]
\draw[-stealth] (0,0) -- (0,3);
\draw[-stealth] (0,0) -- (5,0);

@@

We allow the blocks to share information by placing a hierarchical prior on the collection of $\boldsymbol{\beta}_{k.l}$ where $\mu_p \propto N(0,1)$ and $\sigma_p^2 \sim \mbox{Inv-Gamma}(\alpha_{\sigma},\beta_{\sigma})$.
The cluster assignments are given a non-parameteric prior $z_i \sim \mbox{CRP}(\alpha)$, allowing for a flexible number of clusters.
% TODO: expand on this
